Integer-N Frequency Synthesizer Designed for Settling Time Compliance

### 2025-06-02 CaseStudies/Example3_2_LimitsoftheTheorySoFar/Report/article/article.qmd
Finishing articles .

from IPython.display import display, Markdown

def format_graph(value):
    abs_value = abs(value)
    if abs_value >= 1e9:
        result = f"{value / 1e9:.2f} G"
    elif abs_value >= 1e6:
        result = f"{value / 1e6:.2f} M"
    elif abs_value >= 1e3:
        result = f"{value / 1e3:.2f} k"
    elif abs_value >= 1:
        result = f"{value * 1e0:.2f} "
    elif abs_value >= 1e-3:
        result = f"{value * 1e3:.2f} m"
    elif abs_value >= 1e-6:
        result = f"{value * 1e6:.2f} μ"
    elif abs_value >= 1e-9:
        result = f"{value * 1e9:.2f} n"
    elif abs_value >= 1e-12:
        result = f"{value * 1e12:.2f} p"
    elif abs_value >= 1e-15:
        result = f"{value * 1e15:.2f} f"
    else:
        result = f"{value:.0e} "

    return result
```

from IPython.display import display, Markdown

def format_no_markdown(value):
    abs_value = abs(value)
    if abs_value >= 1e9:
        result = f"{value / 1e9:.2f}\\,\\text{{G}}"
    elif abs_value >= 1e6:
        result = f"{value / 1e6:.2f}\\,\\text{{M}}"
    elif abs_value >= 1e3:
        result = f"{value / 1e3:.2f}\\,\\text{{k}}"
    elif abs_value >= 1:
        result = f"{value * 1e0:.2f}\\,"
    elif abs_value >= 1e-3:
        result = f"{value * 1e3:.2f}\\,\\text{{m}}"
    elif abs_value >= 1e-6:
        result = f"{value * 1e6:.2f}\\,\\mu"
    elif abs_value >= 1e-9:
        result = f"{value * 1e9:.2f}\\,\\text{{n}}"
    elif abs_value >= 1e-12:
        result = f"{value * 1e12:.2f}\\,\\text{{p}}"
    elif abs_value >= 1e-15:
        result = f"{value * 1e15:.2f}\\,\\text{{f}}"
    elif abs_value >= 1e-18:
        result = f"{value * 1e18:.2f}\\,\\text{{a}}"
    else:
        result = f"{value:.0e}\\,"

    return result
```

from IPython.display import display, Markdown

def format(value):
    result = format_no_markdown(value)
    return Markdown(f"${result}$")
```

```{python}
#| echo: false
import math
from IPython.display import display, Markdown

def format_with_pi_latex(value):
    pi_multiple = value / math.pi
    abs_pi_multiple = abs(pi_multiple)

    if abs_pi_multiple >= 1e9:
        result = f"{pi_multiple / 1e9:.2f}\\pi\\,\\text{{G}}"
    elif abs_pi_multiple >= 1e6:
        result = f"{pi_multiple / 1e6:.2f}\\pi\\,\\text{{M}}"
    elif abs_pi_multiple >= 1e3:
        result = f"{pi_multiple / 1e3:.2f}\\pi\\,\\text{{k}}"
    elif abs_pi_multiple >= 1:
        result = f"{pi_multiple:.2f}\\pi"
    elif abs_pi_multiple >= 1e-3:
        result = f"{pi_multiple * 1e3:.2f}\\pi\\,\\text{{m}}"
    elif abs_pi_multiple >= 1e-6:
        result = f"{pi_multiple * 1e6:.2f}\\pi\\,\\mu"
    elif abs_pi_multiple >= 1e-9:
        result = f"{pi_multiple * 1e9:.2f}\\pi\\,\\text{{n}}"
    elif abs_pi_multiple >= 1e-12:
        result = f"{pi_multiple * 1e12:.2f}\\pi\\,\\text{{p}}"
    elif abs_pi_multiple >= 1e-15:
        result = f"{pi_multiple * 1e15:.2f}\\pi\\,\\text{{f}}"
    else:
        result = f"{pi_multiple:.0e}\\pi"

    return Markdown(f"${result}$")

# Exemplo de uso:

@@

It can be observed that the transfer function $H(s)$ presented in \[Eq. @eq-PLL-closed-loop-transfer-function-initial] applies both to the phase of the feedback signal relative to the phase of the reference signal and to the frequency of the feedback signal relative to the frequency of the reference signal.

>>>>

from format_utils import format, format_graph, format_no_markdown, format_with_pi_latex

@@

It can be observed that the transfer function $H(s)$ presented in [Eq. @eq-PLL-closed-loop-transfer-function-initial] applies both to the phase of the feedback signal relative to the phase of the reference signal and to the frequency of the feedback signal relative to the frequency of the reference signal.

### 2025-06-02 CaseStudies/Example3_3_IntegerNSynthesizerDesignedforSettlingTime/article/article.qmd
Finishing articles .

from IPython.display import display, Markdown

def format_graph(value):
    abs_value = abs(value)
    if abs_value >= 1e9:
        result = f"{value / 1e9:.2f} G"
    elif abs_value >= 1e6:
        result = f"{value / 1e6:.2f} M"
    elif abs_value >= 1e3:
        result = f"{value / 1e3:.2f} k"
    elif abs_value >= 1:
        result = f"{value * 1e0:.2f} "
    elif abs_value >= 1e-3:
        result = f"{value * 1e3:.2f} m"
    elif abs_value >= 1e-6:
        result = f"{value * 1e6:.2f} μ"
    elif abs_value >= 1e-9:
        result = f"{value * 1e9:.2f} n"
    elif abs_value >= 1e-12:
        result = f"{value * 1e12:.2f} p"
    elif abs_value >= 1e-15:
        result = f"{value * 1e15:.2f} f"
    else:
        result = f"{value:.0e} "

    return result
```

from IPython.display import display, Markdown

def format(value, decimals=2):
    abs_value = abs(value)
    fmt = f".{decimals}f"

    if abs_value >= 1e9:
        result = f"{value / 1e9:{fmt}}\\,\\text{{G}}"
    elif abs_value >= 1e6:
        result = f"{value / 1e6:{fmt}}\\,\\text{{M}}"
    elif abs_value >= 1e3:
        result = f"{value / 1e3:{fmt}}\\,\\text{{k}}"
    elif abs_value >= 1:
        result = f"{value * 1e0:{fmt}}\\,"
    elif abs_value >= 1e-3:
        result = f"{value * 1e3:{fmt}}\\,\\text{{m}}"
    elif abs_value >= 1e-6:
        result = f"{value * 1e6:{fmt}}\\,\\mu"
    elif abs_value >= 1e-9:
        result = f"{value * 1e9:{fmt}}\\,\\text{{n}}"
    elif abs_value >= 1e-12:
        result = f"{value * 1e12:{fmt}}\\,\\text{{p}}"
    elif abs_value >= 1e-15:
        result = f"{value * 1e15:{fmt}}\\,\\text{{f}}"
    else:
        result = f"{value:.0e}\\,"

    return Markdown(f"${result}$")

@@

```{python}
#| echo: false
import math
from IPython.display import display, Markdown

def format_with_pi_latex(value):
    pi_multiple = value / math.pi
    abs_pi_multiple = abs(pi_multiple)

    if abs_pi_multiple >= 1e9:
        result = f"{pi_multiple / 1e9:.2f}\\pi\\,\\text{{G}}"
    elif abs_pi_multiple >= 1e6:
        result = f"{pi_multiple / 1e6:.2f}\\pi\\,\\text{{M}}"
    elif abs_pi_multiple >= 1e3:
        result = f"{pi_multiple / 1e3:.2f}\\pi\\,\\text{{k}}"
    elif abs_pi_multiple >= 1:
        result = f"{pi_multiple:.2f}\\pi"
    elif abs_pi_multiple >= 1e-3:
        result = f"{pi_multiple * 1e3:.2f}\\pi\\,\\text{{m}}"
    elif abs_pi_multiple >= 1e-6:
        result = f"{pi_multiple * 1e6:.2f}\\pi\\,\\mu"
    elif abs_pi_multiple >= 1e-9:
        result = f"{pi_multiple * 1e9:.2f}\\pi\\,\\text{{n}}"
    elif abs_pi_multiple >= 1e-12:
        result = f"{pi_multiple * 1e12:.2f}\\pi\\,\\text{{p}}"
    elif abs_pi_multiple >= 1e-15:
        result = f"{pi_multiple * 1e15:.2f}\\pi\\,\\text{{f}}"
    else:
        result = f"{pi_multiple:.0e}\\pi"

    return Markdown(f"${result}$")

# Exemplo de uso:

@@

This report presents the design of an integer-N frequency synthesizer operating from `{python} format(f0)`Hz to `{python} format(f, 4)`Hz. The synthesizer is required to achieve frequency settling within a time of $t_s=$ `{python} format(t_s)`s. Given that the channel spacing is `{python} format(f_ref)`Hz and an integer-N architecture is employed, the channel spacing is equal to the reference frequency. This example is based on the methodology and parameters provided in @rogers2006IntegratedCircuitDesign.

@@

For instance, to synthesize a frequency of `{python} format(f_example_1, 3)`Hz, the required control voltage $V_c$ is computed using:

@@

# Parâmetros iniciais
#K_theta = Kphase = I_CP / (2 * np.pi)
A0 = 6.258
#A0 = 1
#K = A0 * Kphase * Kvco / N0
```

# Parâmetros do PLL
#C1 = K / omega_n**2
#C2 = C1 / 10
#R1 = 2 * zeta * omega_n / K
```

@@

@@

Thus, the resistor value is $R=$ `{python} format(R_1)`$\Omega$.

Using a common design heuristic, the second capacitor $C_2$ is:

>>>>

from format_utils import format, format_graph, format_no_markdown, format_with_pi_latex

@@

@@

This report presents the design of an integer-N frequency synthesizer operating from `{python} format(f0)`Hz to `{python} format(f)`Hz. The synthesizer is required to achieve frequency settling within a time of $t_s=$ `{python} format(t_s)`s. Given that the channel spacing is `{python} format(f_ref)`Hz and an integer-N architecture is employed, the channel spacing is equal to the reference frequency. This example is based on the methodology and parameters provided in @rogers2006IntegratedCircuitDesign.

@@

For instance, to synthesize a frequency of `{python} format(f_example_1)`Hz, the required control voltage $V_c$ is computed using:

@@

A0 = 6.258
```

@@

where

$$
K = A_0K_\theta K_\mathrm{VCO}N^{-1}
$$

such that $A_0$ is the DC gain (usually unity), $K_\theta = I / 2\pi$ is the charge pump gain, $K_\mathrm{VCO}$ is the VCO gain, and $N$ is the frequency divider. Furthermore, to align the calculated values with the responses obtained in simulation, an empirical value for the DC gain was determined as $A_0 =$ `{python} round(A0, 2)`.

@@

Thus, the resistor value is $R=$ `{python} format(R_1)`$\Omega$. Using a common design heuristic, the second capacitor $C_2$ is:
